Volatility and the Buyback Anomaly: Interactive Tool

### 2017-03-23 manuscript.Rnw
refactor

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
#dev.off();
#library(knitr); knit2pdf('manuscript.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscript",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists
# Then to make it into Word: 
# system("pandoc -s manuscript.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")

@@

if (generate_all_data == 1){
  source("create_project_data.R")
}
if (generate_rnw_data == 1){
  source("process_data_for_paper.R")
} else {
  load("data_for_paper.Rdata")
}

source("library_files/lib_helpers.R", chdir=TRUE)
source("library_files/latex_code.R")
source("library_files/ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

We find that both the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models explain the equity issue anomaly, but not the buyback anomaly. Moreover, the \cite{FamaFrench2015} model does a better job than the \cite{StambaughYuan2016} one: during the 48 months after the buyback announcement the four factor model produces (statistically significant at the 1$\%$ level) excess returns of \Sexpr{round(CAL_table_all_bb["+48","CAL 5F"],2)}$\%$ per month versus \Sexpr{round(CAL_table_all_bb["+48","CAL 3F"],2)}$\%$  per month with the four factor model.  Unlike other anomalies that disappear over time \citep{McLean2016}, the buyback anomaly persists over time and does not decline in recent years. \cite{PeyerVermaelen2009} show that long terms excess returns are negatively related to firm size, prior return and market to book ratio and summarize these characteristics in an undervaluation index (U-index).  We also show that this conclusion holds for both factor models.

@@

After documenting that volatility as well as standardized idiosyncratic volatility are positively related to long-term excess returns after buybacks we test whether these variables can improve our ability to predict long-term excess returns, above the predictive ability of the undervaluation index (U-index) developed by \cite{PeyerVermaelen2009}. Combining total volatility and standardized idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index) improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high EU-Index portfolio generates an excess return of \Sexpr{round(EU_CALtable_bb["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(EU_IRATStable_bb["+48",19],2)}$\%$ after 48 months. On the other hand, we show that the Mispricing Measure (MM) developed by \cite{Stambaugh2015} on the basis of 11 anomalies is not helpful in predicting long term excess returns after buyback authorization announcements. This again shows that the 11 anomaly indicators that may be relevant for average stocks don't apply to buyback stocks.

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base. We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{BUYBACK_DATA$cleanupNoPermno +  BUYBACK_DATA$cleanupNoCRSPdata + BUYBACK_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(BUYBACK_DATA$cleanupBIZ$Industry_filter)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. Table \ref{tbl:descriptive} summarizes the key data in this study. The average percent of shares authorized for these firms was \Sexpr{datasummaryBB["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryBB["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{datasummaryBB["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryBB["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryBB["BE/ME", "Mean"]} (median of \Sexpr{datasummaryBB["BE/ME", "Median"]}).

For the issuers, we started with \Sexpr{cleanup_iss$Standardise$SDC_initial_data} events from SDC, filtered to exclude rights issues, pure secondary offerings where existing shareholders sell shares without generating proceeds for the company,  issues made by non-U.S. firms or in non-U.S. markets, issues made by closed-end funds or unit investment trusts, as well as block trades, accelerated offers and best efforts. We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases. Finally, as for the buybacks, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{ISSUERS_DATA$cleanupNoPermno +  ISSUERS_DATA$cleanupNoCRSPdata + ISSUERS_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events). We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(ISSUERS_DATA$cleanupBIZ$Industry_filter)} events). Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms. The average percent of shares issued (for the events for which this information was available) was \Sexpr{datasummaryISS["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{datasummaryISS["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{datasummaryISS["Market cap.", "Mean"]} Million (median of \$\Sexpr{datasummaryISS["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{datasummaryISS["BE/ME", "Mean"]} (median of \Sexpr{datasummaryISS["BE/ME", "Median"]}). Note also from Table \ref{tbl:descriptive} that the average and median Mispricing Measure developed by \cite{Stambaugh2015} is higher for equity issuers than for buyback stocks, which is consistent with the hypothesis that equity issuers are more likely to be overvalued than share repurchasers.

@@

The results in Table~\ref{tbl:priorBuybacks}, Panel~A, show that using a five-factor the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{round(IRATS_table_all_bb["+48","CAR 5F"],2)}$\%$ after 4 years (t=\Sexpr{IRATS_table_all_bb["+48",5]}). The results with the 4 factor model are even stronger with excess returns of \Sexpr{round(IRATS_table_all_bb["+48","CAR 3F"],2)}$\%$ (t=\Sexpr{round(IRATS_table_all_bb["+48",2],2)}) after 4 years.  In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback. Consistent with past research [see e.g., \citep{PeyerVermaelen2009}] buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(IRATS_table_all_bb[reported_times[1],1],0)}$\%$. This is consistent with the hypothesis that the typical repurchase announcement is triggered by a stock price decline that insiders may feel is not justified given their long-term prospects about the company.

@@

We sum up these three scores for each firm and we then define as ``high U-index'' the firms with total score more than \Sexpr{quantile(valuation_index_bb,1-quantile_Uindex)} and as ``low U-index'' those with total score less than \Sexpr{quantile(valuation_index_bb,quantile_Uindex)}. Note that unlike \cite{PeyerVermaelen2009} we do not consider the stated reasons for the buyback in the press release, hence we define different thresholds for the high U-index and low U-index buyback firms. We end up with \Sexpr{sum(company_subset_undervalued_bb)} ``high U-index'' buyback stocks (\Sexpr{round(sum(company_subset_undervalued_bb)/length(cusip_bb)*100,2)}\% of all buyback events), and \Sexpr{sum(company_subset_overvalued_bb)} ``low U-index'' ones (\Sexpr{round(sum(company_subset_overvalued_bb)/length(cusip_bb)*100,2)}\% of all buyback events). The distribution of the U-index of all buyback events is shown in Figure~\ref{fig:undervaluationindex}.

@@

The calendar time results confirm the IRATS results. Regardless of the factor model and the investment horizon (24 months and beyond) long-term excess returns are positive a statistically significant at the 1$\%$ level. As in Panel A, excess returns are larger when the Stambaugh-Yuan four factor model is used as a benchmark. Specifically, during the 48-month period after the buyback announcement firms earn excess returns of \Sexpr{round(CAL_table_all_bb["+48","CAL 3F"],2)}$\%$ (t=\Sexpr{round(CAL_table_all_bb["+48",2],2)}) and \Sexpr{round(CAL_table_all_bb_undervaluation["+48","U:CAL3F"],2)}$\%$ (t=\Sexpr{round(CAL_table_all_bb_undervaluation["+48",2],2)}) in the case of high U-index firms.  So we can conclude that the buyback anomaly and the relevance of the U-index survive the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models.

@@

Table~\ref{tbl:priorIssuers}, shows the results for all equity issues. Note that because there is no undervaluation index for equity issues we use the Mispricing Measure (MM) of \cite{Stambaugh2015} to measure overvaluation. Specifically, we define all issuers in the top 20$^{th}$ MM percentile as High MM firms and issuers in the bottom 20$^{th}$ MM percentile as low MM firms. Note that high values of MM correspond to more overvaluation. Table~\ref{tbl:priorIssuers} panel A shows the IRATS results while panel B shows the Calendar Time results.  For the total sample, the Fama-French five factor model fully explains the anomaly, regardless of the method to measure abnormal returns. However, using IRATS, the 4 factor model produces significant positive excess returns of \Sexpr{round(IRATS_table_all_iss["+48","CAR 3F"],2)}$\%$ after 4 years (t=\Sexpr{round(IRATS_table_all_iss["+48",2],2)}). With the calendar time method, the excess returns become less significant (t=\Sexpr{round(CAL_table_all_iss["+48",2],2)}) but have the same magnitude (\Sexpr{round(CAL_table_all_iss["+48","CAL 3F"],2)}$\%$ per month or \Sexpr{48*round(CAL_table_all_iss["+48","CAL 3F"],2)}$\%$  after 48 months). When splitting up the sample according to MM, the Fama-French five factor model shows no significant long-term excess returns regardless of the investment horizon and the method to measure excess returns. A similar result is found when we use the \cite{Stambaugh2015} four factor model and the Calendar Time method.

Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(IRATS_table_all_iss["-6","CAR 3F"],2)}$\%$ in the 6 months prior to the equity issue. However, the lack of post announcement {\it negative} excess returns shows that this was not reflecting ''irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them. In summary, we find no robust evidence that firms issue stock because they are overvalued, irrespective of whether they are High or Low MM firms.

@@

Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time. There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{BBtable_time["+48",10]}$\%$ (t=\Sexpr{BBtable_time["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{BBtable_time_cal["+48",10]}$\%$ per month. This result appears to also be inconsistent with \cite{PeyerVermaelen2009}. However, if one includes the financial sector firms or considers the three-factor model, as \cite{PeyerVermaelen2009} do, the calendar method abnormal returns do become significant.\footnote{Details available upon request.} Note that the period 1991-2000 was a period characterized by a large number of buybacks near the end of the century (Figure 1). During the last two years there were several months with an exceptionally large number of buybacks. High buyback concentration will produce significant differences between IRATS and Calendar Time results.

@@

We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months1,1),1)}$\%$, \Sexpr{round(tail(months3,1),1)}$\%$, \Sexpr{round(tail(months6,1),1)}$\%$, \Sexpr{round(tail(months12,1),1)}$\%$, \Sexpr{round(tail(months24,1),1)}$\%$, \Sexpr{round(tail(months36,1),1)}$\%$ and \Sexpr{round(tail(months48,1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} also allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.

@@

For each event we measure the pre-announce returns volatility with the standard deviation of their daily stock returns over the 6 months prior to the buyback announcement. We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies before the event.  In total we have \Sexpr{sum(High_VOL_eventsBB)} ``high volatility'' buybacks-events and \Sexpr{sum(Low_VOL_eventsBB)} ``low volatility'' ones. In the smaller equity issue sample 804 events are classified as high and low volatility.

@@

Moving on to buybacks, Table~\ref{tbl:VOLunderBB} also shows a strong positive relation between volatility and excess returns independent of the factor model used.  For example, using IRATS and the five factor model the cumulative average abnormal return is only \Sexpr{round(IRATS_table_lowvol_BB["+48","CAR 5F"],2)}$\%$  (t=\Sexpr{round(IRATS_table_lowvol_BB["+48",5],2)}) after 48 months in the low volatility sample and \Sexpr{round(IRATS_table_highvol_BB["+48","CAR 5F"],2)}$\%$ (t=\Sexpr{round(IRATS_table_highvol_BB["+48",5],2)}) in the high volatility sample. This time the calendar time method confirms the IRATS result: insignificant monthly excess returns of \Sexpr{round(CAL_table_lowvol_BB["+48","CAL 5F"],2)}$\%$  (t=\Sexpr{round(CAL_table_lowvol_BB["+48",5],2)}) in the low volatility sample versus significant positive monthly excess returns of \Sexpr{round(CAL_table_highvol_BB["+48","CAL 5F"],2)}$\%$ (t=\Sexpr{round(CAL_table_highvol_BB["+48",5],2)}) in the high volatility sample.

@@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
Descriptive_stats_BB1 <- apply(Descriptive_stats_BB,2,function(r) as.character(round(r,2)))
rownames(Descriptive_stats_BB1) <- rownames(Descriptive_stats_BB)
Descriptive_stats_BB1 = rbind(Descriptive_stats_BB1,rep(length(BUYBACK_DATA$DATASET$SDC$CUSIP), 5))
rownames(Descriptive_stats_BB1)[nrow(Descriptive_stats_BB1)] <- "Observations"
colnames(Descriptive_stats_BB1) <- NULL

>>>>

% Style files dependencies:
% - http://faculty.haas.berkeley.edu/stanton/texintro/jf/jf.bst
% - http://faculty.haas.berkeley.edu/stanton/texintro/rfs/rfs.sty
% - http://faculty.haas.berkeley.edu/stanton/texintro/sty/versionPO.sty

<< eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
# dev.off();
# library(knitr); knit2pdf('manuscript.Rnw', texi2dvi='texi2dvi'); file.remove(paste("manuscript",c(".aux",".tex",".blg",".bbl",".log",".out"),sep=""))
#dir.create("tmpfiles") # need to comment this if the directory already exists
# Then to make it into Word: 
# system("pandoc -s manuscript.tex --bibliography=bibliography.bib --number-sections --reference-links -o theo.docx")

@@

if (generate_all_data == 1){
  source("create_project_data.R")
}
if (generate_rnw_data == 1){
  source("process_data_for_paper.R")
}

load("data_for_paper.Rdata")

source("helpers/lib_helpers.R", chdir=TRUE)
source("helpers/latex_code.R")
source("helpers/ff_industries_sic.R")
source("Paper_global_parameters.R")

@@

We find that both the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models explain the equity issue anomaly, but not the buyback anomaly. Moreover, the \cite{FamaFrench2015} model does a better job than the \cite{StambaughYuan2016} one: during the 48 months after the buyback announcement the four factor model produces (statistically significant at the 1$\%$ level) excess returns of \Sexpr{round(buyback_announcements_table$CAL$all["+48","CAL 5F"],2)}$\%$ per month versus \Sexpr{round(buyback_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$  per month with the four factor model.  Unlike other anomalies that disappear over time \citep{McLean2016}, the buyback anomaly persists over time and does not decline in recent years. \cite{PeyerVermaelen2009} show that long terms excess returns are negatively related to firm size, prior return and market to book ratio and summarize these characteristics in an undervaluation index (U-index).  We also show that this conclusion holds for both factor models.

@@

After documenting that volatility as well as standardized idiosyncratic volatility are positively related to long-term excess returns after buybacks we test whether these variables can improve our ability to predict long-term excess returns, above the predictive ability of the undervaluation index (U-index) developed by \cite{PeyerVermaelen2009}. Combining total volatility and standardized idiosyncratic volatility with the \cite{PeyerVermaelen2009} Undervaluation Index into an Enhanced Undervaluation Index (EU-Index) improves the predictability of excess returns. In particular, during the four years following the buyback announcement, the high EU-Index portfolio generates an excess return of \Sexpr{round(buybacks_eu_tables$CAL["+48",13+6],2)}$\%$ per month with the Calendar Time event study method. Using the IRATS method the cumulative excess return reaches \Sexpr{round(buybacks_eu_tables$IRATS["+48",19],2)}$\%$ after 48 months. On the other hand, we show that the Mispricing Measure (MM) developed by \cite{Stambaugh2015} on the basis of 11 anomalies is not helpful in predicting long term excess returns after buyback authorization announcements. This again shows that the 11 anomaly indicators that may be relevant for average stocks don't apply to buyback stocks.

@@

For the buybacks we combined all open market repurchase announcements from both the SDC Repurchases data base and the SDC US mergers and acquisitions ($M\&A$) data base. We ended up with a total of \Sexpr{cleanup_bb$Standardise$final_merge_data} repurchases events, out of which \Sexpr{cleanup_bb$Standardise$only_repurchase_deals} were only from the SDC Repurchases database, \Sexpr{cleanup_bb$Standardise$only_MA_deals} only from the SDC $M\&A$ database and \Sexpr{cleanup_bb$Standardise$overlap_deals} from both. Finally, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{BUYBACK_DATA$cleanupNoPermno +  BUYBACK_DATA$cleanupNoCRSPdata + BUYBACK_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_bb$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_bb$biz_clean$Penny_stock_filter} events), or  the primary stock exchange was not the NYSE, the Nasdaq, or Amex (\Sexpr{cleanup_bb$biz_clean$major_markets_only} events).  Finally, we removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(BUYBACK_DATA$cleanupBIZ$Industry_filter)}  events).\footnote{We are using the industries from Kenneth French's Website. The Financial Sector consists of all firms with SIC code at the time of the buyback announcement that belonged in the ``Banks'' or ``Fin'' industries (SIC codes 6000 to 6300 and 6700 to 6799). The Utilities Sector consists of all firms with SIC code 4900 to 4942.}  At the end we are left with \Sexpr{length(cusip_bb)} buyback events made by \Sexpr{length(unique(cusip_bb))} firms. Table \ref{tbl:descriptive} summarizes the key data in this study. The average percent of shares authorized for these firms was \Sexpr{data_summary$bb["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{data_summary$bb["Percent authorized", "Median"]}$\%$), the average Market Capitalization at announcement was \$\Sexpr{data_summary$bb["Market cap.", "Mean"]} Million (median of \$\Sexpr{data_summary$bb["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{data_summary$bb["BE/ME", "Mean"]} (median of \Sexpr{data_summary$bb["BE/ME", "Median"]}).

For the issuers, we started with \Sexpr{cleanup_iss$Standardise$SDC_initial_data} events from SDC, filtered to exclude rights issues, pure secondary offerings where existing shareholders sell shares without generating proceeds for the company,  issues made by non-U.S. firms or in non-U.S. markets, issues made by closed-end funds or unit investment trusts, as well as block trades, accelerated offers and best efforts. We removed all SDC events for which either the event date (\Sexpr{cleanup_iss$Standardise$SDC_NODATE} events) or the CUSIP (\Sexpr{cleanup_iss$Standardise$SDC_NOCUSIP} events) was missing or where we found duplicate events with mismatching information (\Sexpr{cleanup_iss$Standardise$BAD_DUPLICATES} events), a total of \Sexpr{cleanup_iss$Standardise$SDC_standardize_removal} events - given the overlap between these cases. Finally, as for the buybacks, we removed the following events: no CRSP returns or not all Compustat data available (\Sexpr{ISSUERS_DATA$cleanupNoPermno +  ISSUERS_DATA$cleanupNoCRSPdata + ISSUERS_DATA$cleanupMissingSomeValues} events); the percent of shares authorized was larger than \Sexpr{MAX_EVENT_SIZE}$\%$ (\Sexpr{cleanup_iss$biz_clean$EventSize_filter} events), or the closing price was less than \$\Sexpr{penny_stock_price_old} for events before 1995 or \$\Sexpr{penny_stock_price_recent} for the other (\Sexpr{cleanup_iss$biz_clean$Penny_stock_filter} events), or  the stocks were not listed on the NYSE, Nasdaq or Amex (\Sexpr{cleanup_iss$biz_clean$major_markets_only} events). We again removed all events from firms in the Financial and Utilities sectors (\Sexpr{sum(ISSUERS_DATA$cleanupBIZ$Industry_filter)} events). Our final sample contains \Sexpr{length(cusip_iss)} events made by \Sexpr{length(unique(cusip_iss))} firms. The average percent of shares issued (for the events for which this information was available) was \Sexpr{data_summary$iss["Percent authorized", "Mean"]}$\%$ (median of \Sexpr{data_summary$iss["Percent authorized", "Median"]}$\%$), the average Market Capitalization on the announcement day  was \$\Sexpr{data_summary$iss["Market cap.", "Mean"]} Million (median of \$\Sexpr{data_summary$iss["Market cap.", "Median"]} Million), while the BE/ME was on average \Sexpr{data_summary$iss["BE/ME", "Mean"]} (median of \Sexpr{data_summary$iss["BE/ME", "Median"]}). Note also from Table \ref{tbl:descriptive} that the average and median Mispricing Measure developed by \cite{Stambaugh2015} is higher for equity issuers than for buyback stocks, which is consistent with the hypothesis that equity issuers are more likely to be overvalued than share repurchasers.

@@

The results in Table~\ref{tbl:priorBuybacks}, Panel~A, show that using a five-factor the excess returns are statistically significantly positive over all investment horizons and reach \Sexpr{round(buyback_announcements_table$IRATS$all["+48","CAR 5F"],2)}$\%$ after 4 years (t=\Sexpr{buyback_announcements_table$IRATS$all["+48",5]}). The results with the 4 factor model are even stronger with excess returns of \Sexpr{round(buyback_announcements_table$IRATS$all["+48","CAR 3F"],2)}$\%$ (t=\Sexpr{round(buyback_announcements_table$IRATS$all["+48",2],2)}) after 4 years.  In all the tables we also calculate cumulative excess returns in the 6 months prior to the buyback. Consistent with past research [see e.g., \citep{PeyerVermaelen2009}] buyback authorization announcements are preceded by significant negative excess returns of around \Sexpr{round(buyback_announcements_table$IRATS$all[reported_times[1],1],0)}$\%$. This is consistent with the hypothesis that the typical repurchase announcement is triggered by a stock price decline that insiders may feel is not justified given their long-term prospects about the company.

@@

We sum up these three scores for each firm and we then define as ``high U-index'' the firms with total score more than \Sexpr{quantile(valuation_index_bb,1-quantile_Uindex)} and as ``low U-index'' those with total score less than \Sexpr{quantile(valuation_index_bb,quantile_Uindex)}. Note that unlike \cite{PeyerVermaelen2009} we do not consider the stated reasons for the buyback in the press release, hence we define different thresholds for the high U-index and low U-index buyback firms. We end up with \Sexpr{sum(company_subset$bb$undervalued)} ``high U-index'' buyback stocks (\Sexpr{round(sum(company_subset$bb$undervalued)/length(cusip_bb)*100,2)}\% of all buyback events), and \Sexpr{sum(company_subset$bb$overvalued)} ``low U-index'' ones (\Sexpr{round(sum(company_subset$bb$overvalued)/length(cusip_bb)*100,2)}\% of all buyback events). The distribution of the U-index of all buyback events is shown in Figure~\ref{fig:undervaluationindex}.

@@

The calendar time results confirm the IRATS results. Regardless of the factor model and the investment horizon (24 months and beyond) long-term excess returns are positive a statistically significant at the 1$\%$ level. As in Panel A, excess returns are larger when the Stambaugh-Yuan four factor model is used as a benchmark. Specifically, during the 48-month period after the buyback announcement firms earn excess returns of \Sexpr{round(buyback_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$ (t=\Sexpr{round(buyback_announcements_table$CAL$all["+48",2],2)}) and \Sexpr{round(buyback_announcements_table$CAL$undervaluation["+48","U:CAL3F"],2)}$\%$ (t=\Sexpr{round(buyback_announcements_table$CAL$undervaluation["+48",2],2)}) in the case of high U-index firms.  So we can conclude that the buyback anomaly and the relevance of the U-index survive the \cite{FamaFrench2015} and \cite{StambaughYuan2016} models.

@@

Table~\ref{tbl:priorIssuers}, shows the results for all equity issues. Note that because there is no undervaluation index for equity issues we use the Mispricing Measure (MM) of \cite{Stambaugh2015} to measure overvaluation. Specifically, we define all issuers in the top 20$^{th}$ MM percentile as High MM firms and issuers in the bottom 20$^{th}$ MM percentile as low MM firms. Note that high values of MM correspond to more overvaluation. Table~\ref{tbl:priorIssuers} panel A shows the IRATS results while panel B shows the Calendar Time results.  For the total sample, the Fama-French five factor model fully explains the anomaly, regardless of the method to measure abnormal returns. However, using IRATS, the 4 factor model produces significant positive excess returns of \Sexpr{round(issuers_announcements_table$IRATS$all["+48","CAR 3F"],2)}$\%$ after 4 years (t=\Sexpr{round(issuers_announcements_table$IRATS$all["+48",2],2)}). With the calendar time method, the excess returns become less significant (t=\Sexpr{round(issuers_announcements_table$CAL$all["+48",2],2)}) but have the same magnitude (\Sexpr{round(issuers_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$ per month or \Sexpr{48*round(issuers_announcements_table$CAL$all["+48","CAL 3F"],2)}$\%$  after 48 months). When splitting up the sample according to MM, the Fama-French five factor model shows no significant long-term excess returns regardless of the investment horizon and the method to measure excess returns. A similar result is found when we use the \cite{Stambaugh2015} four factor model and the Calendar Time method.

Note also that equity issues are typically preceded by large positive excess returns of around \Sexpr{round(issuers_announcements_table$IRATS$all["-6","CAR 3F"],2)}$\%$ in the 6 months prior to the equity issue. However, the lack of post announcement {\it negative} excess returns shows that this was not reflecting ''irrational exuberance'' but rather that, for example, these firms possibly experienced a substantial increase in growth opportunities and issued equity to finance them. In summary, we find no robust evidence that firms issue stock because they are overvalued, irrespective of whether they are High or Low MM firms.

@@

Table~\ref{tbl:PastFindingsTimeBB} shows that, regardless of the time period chosen or the method to calculate excess returns, the buyback anomaly remains economically and statistically significant and there is no clear time trend in the data that suggests that markets have become more efficient over time. There is one exception to the consistency between the IRATS and the Calendar Time results: in the period of 1991-2000, the IRATS method generates excess returns after 48 months of \Sexpr{buyback_returns_periods_table$IRATS["+48",10]}$\%$ (t=\Sexpr{buyback_returns_periods_table$IRATS["+48",11]}) but the Calendar Time method produces statistically insignificant excess returns of \Sexpr{buyback_returns_periods_table$CAL["+48",10]}$\%$ per month. This result appears to also be inconsistent with \cite{PeyerVermaelen2009}. However, if one includes the financial sector firms or considers the three-factor model, as \cite{PeyerVermaelen2009} do, the calendar method abnormal returns do become significant.\footnote{Details available upon request.} Note that the period 1991-2000 was a period characterized by a large number of buybacks near the end of the century (Figure 1). During the last two years there were several months with an exceptionally large number of buybacks. High buyback concentration will produce significant differences between IRATS and Calendar Time results.

@@

We report the returns (unhedged strategy) and excess returns (hedged strategy) of such a portfolio strategy for different holding months $N$ = 1, 3, 6, 12, 24, 36, 48 in Figure~\ref{fig:ReturnsBB}.\footnote{Results for other holding periods, as in Figure~\ref{fig:ReturnsBB}, are available upon request.} The basic conclusion is that the shorter the investment horizon the larger the excess returns. Specifically, at the end of \Sexpr{lastyear} the cumulative excess returns from the 1 month, 6 month, 12 month, 24 month, 36 month and 48 month holding periods are respectively equal to \Sexpr{round(tail(months[["1"]],1),1)}$\%$, \Sexpr{round(tail(months[["3"]],1),1)}$\%$, \Sexpr{round(tail(months[["6"]],1),1)}$\%$, \Sexpr{round(tail(months[["12"]],1),1)}$\%$, \Sexpr{round(tail(months[["24"]],1),1)}$\%$, \Sexpr{round(tail(months[["36"]],1),1)}$\%$ and \Sexpr{round(tail(months[["48"]],1),1)}$\%$. This is not surprising as the Calendar Time results in Table~\ref{tbl:priorBuybacks} show that the monthly excess returns decline when the investment horizon becomes longer. However, Figure~\ref{fig:ReturnsBB} also allows us to verify that the excess returns are not simply the result of outperformance during a particular time period.

@@

For each event we measure the pre-announce returns volatility with the standard deviation of their daily stock returns over the 6 months prior to the buyback announcement. We define two types of events: ``low volatility'' and ``high volatility'' events, depending on whether volatility was in the top or bottom \Sexpr{round(100*quantile_VOL,2)}$\%$ of the volatilities of all CRSP companies before the event.  In total we have \Sexpr{sum(VOL_events$bb$highvol)} ``high volatility'' buybacks-events and \Sexpr{sum(VOL_events$bb$lowvol)} ``low volatility'' ones. In the smaller equity issue sample 804 events are classified as high and low volatility.

@@

Moving on to buybacks, Table~\ref{tbl:VOLunderBB} also shows a strong positive relation between volatility and excess returns independent of the factor model used.  For example, using IRATS and the five factor model the cumulative average abnormal return is only \Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$lowvol["+48","CAR 5F"],2)}$\%$  (t=\Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$lowvol["+48",5],2)}) after 48 months in the low volatility sample and \Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$highvol["+48","CAR 5F"],2)}$\%$ (t=\Sexpr{round(buybacks_issuers_volatility_table$IRATS$bb$highvol["+48",5],2)}) in the high volatility sample. This time the calendar time method confirms the IRATS result: insignificant monthly excess returns of \Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$lowvol["+48","CAL 5F"],2)}$\%$  (t=\Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$lowvol["+48",5],2)}) in the low volatility sample versus significant positive monthly excess returns of \Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$highvol["+48","CAL 5F"],2)}$\%$ (t=\Sexpr{round(buybacks_issuers_volatility_table$CAL$bb$highvol["+48",5],2)}) in the high volatility sample.

@@

<<   eval = TRUE, echo=FALSE,message=FALSE,fig.pos='h',results='asis' >>=
descriptive_stats$bb1 <- apply(descriptive_stats$bb,2,function(r) as.character(round(r,2)))
rownames(descriptive_stats$bb1) <- rownames(descriptive_stats$bb)
descriptive_stats$bb1 = rbind(descriptive_stats$bb1,rep(length(BUYBACK_DATA$DATASET$SDC$CUSIP), 5))
rownames(descriptive_stats$bb1)[nrow(descriptive_stats$bb1)] <- "Observations"
colnames(descriptive_stats$bb1) <- NULL
